Brief Article

### 2012-02-14 power.tex
strength of dataplot

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_B$. The grey line shows probability of picking the data plot under $H_0$. We see that for a $p$ value $p_B$ of about 0.15 for the dataplot the signal in the plot is so weak, that we cannot distinguish the dataplot from nullplots in a lineup of size $m=20$. (Mahbub, is that what we see in practice?)}
   \label{power}
\end{figure}
Under $H_1$ we therefore get an estimate for the strength of the dataplot signal $p_B$ as
\[
\widehat{E[p_B]} = 1 - \left( \frac{n_m}{K} \right)^{1/(m-1)}.
\]
Similarly, we get an estimate for $E[X]$, the average number of null plots with a stronger signal strength than the data plot as the number of nullplots in the lineup with more than $n_m$ picks in their favor, which leads us to another estimate of $E[p_B]$ as 
\[
\widehat{E[p_B]}  = 1 - 1/(m-1) \cdot \sum_i I (n_i > n_m),
\]
where $I(x) = 1$ for $x$ is true and $I(x) = 0$ if $x$ is false.
\end{document}

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_B$. The grey line shows probability of picking the data plot under $H_0$. We see that for a $p$ value $p_B$ of about 0.15 for the dataplot the signal in the plot is so weak, that we cannot distinguish the dataplot from nullplots in a lineup of size $m=20$. (Mahbub, is that what we see in practice?)}
   \label{power}
\end{figure}
Based on $K$ observers, we can assume that $n_m$ votes for the dataplot represent support for the data over any of the nullplots, i.e. $\pi_m = P(X=0)$.

Under $H_1$ we therefore get an estimate for the strength of the dataplot signal $p_B$ as
\[
\widehat{E[p_B]} = 1 - \left( \frac{n_m}{K} \right)^{1/(m-1)}.
\]
%Similarly, we get an estimate for $E[X]$, the average number of null plots with a stronger signal strength than the data plot as the number of nullplots in the lineup with more than $n_m$ picks in their favor, which leads us to another estimate of $E[p_B]$ as 
%\[
%\widehat{E[p_B]}  = 1 - 1/(m-1) \cdot \sum_i I (n_i > n_m),
%\]
%where $I(x) = 1$ for $x$ is true and $I(x) = 0$ if $x$ is false.
\end{document}
